---
title: "diamonds"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

```

reading the data set
```{r}
jems <- read_csv("data/diamonds.csv")
```

Explore the data set
```{r}
summary(jems)

str(jems)

glimpse(jems)

dim(jems)

names(jems)

rownames(jems)

nrow(jems)

jems %>% 
head(5)

jems %>% 
  tail(5)
```

How many diamonds with a clarity of category “IF” are present in the data-set?
```{r}

jems %>% 
  filter(clarity == "IF") -> clarity_IF
clarity_IF
```

What fraction of the total do they represent?
```{r}

nrow(clarity_IF)/ nrow(jems)
  
```

What proportion of the whole is made up of each category of clarity?
```{r}

jems %>% 
  group_by(clarity) %>% 
  summarise(mean(price))
```

What is the cheapest diamond price overall? 
```{r}
min(jems$price)

```

What is the range of diamond prices?
```{r}
range(jems$price)
```

What is the average diamond price in each category of cut and color?
```{r}

jems %>% 
  group_by(cut, color) %>% 
  summarise(mean(price))
```


Make a scatter plot that shows the price of a diamond as described by another continous variable, like the carat.
```{r}
ggplot(jems, aes(x= carat, y=price)) + 
  geom_point()
```

using the functions we discuss earlier, and in class, apply a log10 transformation to both the price and carat. 

```{r}
jems3 <- jems %>%
  mutate(log10_price = log10(price),
         log10_carat = log10(carat))
ggplot(jems3, aes(x= log10_carat, y=log10_price)) +
  geom_point() +
  geom_smooth(method = "lm")
```


to recreate a model that describes the relatioship shown in the plot
```{r}
jems_lm <- lm(log10_price  ~  log10_carat, data= jems3)

```

Now that we’ve described the diamond price given a single variable, can you display that on the plot? Try to use the geom_smooth() function to add this new layer.

```{r}
ggplot(jems3, aes(x= log10_carat, y=log10_price)) + 
  geom_point() +
  geom_smooth(method = "lm")

```





